---
title: "ENVS-193DS_homework-03"
author: "Ethan Mathews"
date: "05/24/2025"
format: html
---

link to GitHub Repository: https://github.com/ethan-mathews24/ENVS-193DS_homework-03.git

```{r Reading in Packages}

#| message: false

library(tidyverse)

library(gt)

library(janitor)

library(here)

library(readxl)

data <- read.csv("data/PersonalStudyHome.csv")

```


##Part 2. Problems 

###Problem 1. Personal Data 


####a. 

The data can be summarized by comparing the distribution of water consumption (liters) between cardiovascular and strength training workouts using a box plot with underlying data shown as jitter points. This comparison is informative because cardiovascular workouts are typically more physically demanding and sweat-intensive, potentially leading to greater water intake than strength training sessions, which often occur in more controlled environments. 


####b.
```{r Personal Data Visualization}





```


####c. 
Caption Here --- 




####d.
```{r Data Table Visualization}






```



### Problem 2. Affective visualization










